\documentclass[10pt,letterpaper,roman]{moderncv}	% possible options include font size, paper size, and font family
\usepackage{color}
\usepackage{verbatim}
\usepackage[top=1in, bottom=.75in, left=1in, right=1in]{geometry}
\moderncvstyle{banking}	% style options are 'casual', 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red}	% color options 'blue', 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\nopagenumbers{}
\usepackage[scale=0.75]{geometry}	% adjusts page margins
\setlength{\hintscolumnwidth}{3cm}	% width of date column
\name{\textcolor{black}{Benjamin}}{\textcolor{black}{Lorenzetti}}
%\title{Resume Title}	% optional, remove / comment the line if not wanted
\address{1302 Ponderosa Ct}{Fairborn, OH 45324}{}	% each individual part is optional: 
							%{Address 1}{city, state zip}{country}
\phone[mobile]{+1~(937)~522~1673}	% the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
%\phone[fixed]{+2~(345)~678~901}
%\phone[fax]{+3~(456)~789~012}
\email{lorenzbn@mail.uc.edu}
%\homepage{www.benlorenzetti.com}
%\social[linkedin]{john.doe}
%\social[twitter]{jdoe}
%\social[github]{jdoe}
%\extrainfo{additional information}
%\photo[64pt][0.4pt]{resume-photo}	% optional, remove / comment the line if not wanted; 
					%'64pt' is the height the picture must be resized to, 
					%0.4pt is the thickness of the frame around it (put 
					%it to 0pt for no frame) and 'picture' is the name of 
					%the picture file
\begin{document}
\makecvtitle

\section{Education}
% {date--date}{Degree}{Institution}{City}{\textit{Grade}}{Description}
\cventry{2013--Dec. 2016}{Pursuing BS in Electrical Engineering, Minor in Chemistry}{University of Cincinnati}{Cincinnati, OH}{\textit{3.56/4.00}}{
Previously pursuing BS in Mechanical Engineering \hfill 2010--2012
}
%\cventry{2010--2012}{Previously pursuing BS in Mechanical Engineering}{University of Cincinnati}{}{}{}
\cventry{2006--2010}{High School Diploma}{Fairborn High School}{Fairborn, OH}{\textit{4.0/4.0}}{}

\section{Experience}

\cventry{Summer 2015}{Manufacturing Engineering Co--op}{Proctor \& Gamble Duracell}{Cleveland, TN}{}{
Managed several engineering projects at the C\&D cell make plant and the packaging center:
\begin{itemize}
\item New collaborative robot palletizers (CoPals) for Lines 285 and 291.
	\begin{itemize}
	\item POC with vendors, design reviews, capacity study, VAT plan, training plan, safety req., installation plan.
	\item Organized cross--disciplinary team of line technicians, E\&I technicians, HS\&E, procurement, and engineering. 
	\end{itemize}
\item Replacement of Lifetest PLC and thermocouples (scope of work and quotations)
\item Survey of new packaging technologies (brought in several vendors and held presentation for management)
\item Held successful culture, morale, and safety event with other Co--ops
\end{itemize}
}

\cventry{Fall, Spring 2014}{Research Co--op}{University of Cincinnati BioMicroSystems Lab}{Cincinnati, OH}{}{
Responsible for improving user interface of electrochemical, analytic sensors being developed at UC.
\begin{itemize}
\item Designed PCB for interfacing commercial potentiostat with Pb \& Mn sensors
\item Built enclosure for potentiostat/PCB
\item Wrote software GUI in C/C++, utilitzing libusb, Berkley Sockets, and pthreads library
\end{itemize}}

\cventry{Spring, Fall 2012}{Materials Research Co--op}{Toyota Technical Center}{Ann Arbor, MI}{}{
Fabricated superparamagnetic nanoparticle compacts and optimized their bulk-magnetic properties.
\begin{itemize}
\item Improved oxygen-free enclosure for transporting air-sensitive nanoparticles
\item Developed sintering/annealing technique for \(Permendur/SiO_{2}\) core/shell nanoparticles
\item Managed day-to-day maintenance and chemical inventory of Lab M2
\item Oversaw installation of vibrating sample magnetometer (VSM) and authored TTC operating manual
\end{itemize}}

\cventry{Summer 2011}{Engineering Intern}{Tec\^ Edge Discover Lab}{Dayton, OH}{}{
Compared various commercial technologies for their potential to generate power in remote locations
}

\section{Technical Skills}
\cvitem{Languages and Libraries}{C, C++, libusb, pthreads, MathGL, \LaTeX, MATLAB, HTML5, CSS3}{}{}
\cvitem{Tools}{CadSoft Eagle, KiCad, NGSPICE, DraftSight, SolidWorks, Apache, Postfix}{}{}

\section{Honors and Awards}
Eagle Scout Award, National Merit Scholar, UC|21 Scholar, Elks Most Valuable Student Scholar

\pagebreak

\section{Community Involvement}
\cventry{2010--2015}{UC Breakfast Brigade}{St. Monica St. George Parish}{Cincinnati, OH}{}{
Breakfast brigade is a service organization sponsored by St. Monica St. George Catholic Church. We prepare breakfast for day laborers in Cincinnati, who rarely have enough time to eat between reporting at their agency and commuting to work assignments. Breakfast is served every Thursday, 4:30--5:00 a.m., at Labor Works Cincinnati.
}

\section{Personal Projects}
\cventry{}{https://github.com/benlorenzetti/Breadboarding-Oven}{Easy--PCB Oven}{}{}{
A homemade convection oven for paste soldering SMD and BGA components.
}

%\section{References}
%\begin{cvcolumns}
%  \cvcolumn{Category 1}{\begin{itemize}\item Person 1\item Person 2\item Person 3\end{itemize}}
%  \cvcolumn{Category 2}{Amongst others:\begin{itemize}\item Person 1, and\item Person 2\end{itemize}(more upon request)}
%  \cvcolumn[0.5]{All the rest \& some more}{\textit{That} person, and \textbf{those} also (all available upon request).}
%\end{cvcolumns}

\begin{comment}

\clearpage
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
\date{January 01, 1984}
\opening{Dear Sir or Madam,}
\closing{Sincerely,}
%\enclosure[Attached]{curriculum vit\ae{}}	% use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

Paragraph 1.

Paragraph 2.

Paragraph 3.

\makeletterclosing

\end{comment}

\end{document}
